---
title: "Estimation_of_Mean"
author: "virgile"
date: "02/01/2015"
output: html_document
---

Example from Michael A. McCarthy's book: [Bayesian Methods for Ecology](http://www.cambridge.org/us/academic/subjects/life-sciences/ecology-and-conservation/bayesian-methods-ecology)

The second example in the book is the estimation of the average diameter of trees in an eucalypt forest.


#### First, we upload the data: 

Here we have 10 measures of tree diameters. To fit it with rstan, we create a `list()`.

```{r}
diam_tree=c(42,43,58,70,47,51,85,63,58,46)
model_2_data=list(Y=diam_tree,N=length(diam_tree))
```

Information on data:

```{r}
mean(diam_tree)
sd(diam_tree)
```

### Bayesian estimation:

We have to write a file name here `model_2.stan` were we write:

```{r,echo=FALSE}
data {
  int<lower=0> N; // number of data 
  real Y[N]; // mean of tree
}
parameters {
  real m; // prior for the mean
  real stdev; // prior for the standard deviation
}
transformed parameters {
   real prec; // precision of the data = 1/variance
  prec <- 1/(stdev*stdev)
}
model {
   m ~ normal(0,1e3); // uninformative prior (very large)
  // stdev ~ sd(Y);
  Y ~ normal(m,prec);
}
```

Here are some graph illustrating the prior distributions:

```{r}
hist(rnorm(1e6,0,1e3),breaks=100)
```

```{r}
library(rstan)
```

```{r}
fit_model_2 <- stan(file="model_2.stan", data=model_2_data,iter=1e4, chains=3,warmup=5e3)
```

```{r}
print(fit_model_2)
```

Plotting the trace plots:

```{r}
traceplot(fit_model_2)
```

And the parameter distribution:

```{r}
plot(fit_model_2)
```



How to plot posterior and so on:

```{r}
s=extract(fit_model_2,pars = c("m","prec"))
plot(density(s$m))





x <- seq(-max(s$m), max(s$m), length=1e3)
hx <- dnorm(x,0,1e3)
plot(x,hx,type='l')

for (i in 1:4){
  lines(x, dt(x,degf[i]), lwd=2, col=colors[i])
}

legend("topright", inset=.05, title="Distributions",
  labels, lwd=2, lty=c(1, 1, 1, 1, 2), col=colors)
curve()
```

